---
title: "2022 Temperature Overview: Loggers"
output: html_document
date: "`r Sys.Date()`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = 'C:/Users/Geissingere/Documents/Projects/Temperature-Project/')
library(tidyverse)
library(lubridate)
library(leaflet)
```


```{r data upload, echo = FALSE}
loggers <- read.csv("./data-working/output/logger-data-2022-full.csv") |> 
  separate(Date.Time, into = c("Date", "Time"), sep = " ") |> 
  mutate(Time = replace(Time, is.na(Time), "00:00:00")) |> 
  mutate(Date.Time = ymd_hms(paste(Date, Time))) |> 
  mutate(Date.deployed = mdy(Date.deployed.MDY),
         Time.deployed = ymd_hm(paste(Date.deployed, Time.deployed)))
stations <- read.csv( "./data-working/Loggers_2022.csv",
                     skip = 1,
                     header = TRUE) |>
  rename(Logger.Type = "Logger.Type.Note..minilog...level.are.not.bluetooth") |>
  dplyr::select( River,
                 Lat, 
                 Long, 
                 Date.deployed.MDY, 
                 Time.deployed, 
                 Recording,Serial, 
                 Logger.Type,
                 Depth.cm, 
                 Date.Downloaded,
                 Location.description, 
                 Deployed.by,
                 Notes) |>
  mutate(Lat = as.numeric(Lat),
         Long = as.numeric(Long),
         Serial = as.integer(Serial))

stillout <- stations |>
  filter(!Serial %in% loggers$Serial) |>
  filter(Logger.Type != "Cellular Station" & Logger.Type != "Wifi Station")

```

Need to add SFAs and river numbers to 2022 data before proceeding



```{r site map, echo = FALSE}
leaflet() |>
  setView(lng = -55.67, lat=48.93, zoom=5 ) |>
  addTiles() |>
  addCircleMarkers(data = stillout |> 
                     distinct(Serial, River, Lat, Long),
                   color = 'grey',
                   popup = ~paste0(River,
                              "<br>SN: ", Serial,
                              "<br>Lat: ", Lat,
                              "<br>Long: ", Long),
                   radius = 5,
                   stroke = TRUE,
                   weight = 1,
                   fillOpacity = .8) |> 
  addCircleMarkers(data = loggers |> 
                     filter(Recording == "Water") |> 
                     distinct(Serial, River, Lat, Long),
                   color = 'blue',
                   popup = ~paste0(River,
                              "<br>SN: ", Serial,
                              "<br>Lat: ", Lat,
                              "<br>Long: ", Long),
                   radius = 5,
                   stroke = TRUE,
                   weight = 1,
                   fillOpacity = .8) |> 
  addCircleMarkers(data = loggers |> 
                     filter(Recording == "Air") |> 
                     distinct(Serial, River, Lat, Long),
                   color = 'green',
                   popup = ~paste0(River,
                              "<br>SN: ", Serial,
                              "<br>Lat: ", Lat,
                              "<br>Long: ", Long),
                   radius = 5,
                   stroke = TRUE,
                   weight = 1,
                   fillOpacity = .8) |> 
  addCircleMarkers(data = loggers |> 
                     filter(Recording == "Level") |> 
                     distinct(Serial, River, Lat, Long),
                   color = 'purple',
                   popup = ~paste0(River,
                              "<br>SN: ", Serial,
                              "<br>Lat: ", Lat,
                              "<br>Long: ", Long),
                   radius = 5,
                   stroke = TRUE,
                   weight = 1,
                   fillOpacity = .8) |> 
  addScaleBar(position = "bottomright") |> 
  addLegend(position = "topright",
            colors = c("blue", "green", "purple","grey"),
            labels = c("Water", "Air", "Level","Data not retreived in 2022"))
  

```


Check if loggers are out of water by comparing to air loggers.
If water loggers are within XX of daily mix and max of air loggers, then it will be considered out of water
Ideally, will be able to do this statistically, but for now will use current method
```{r out of water checks, echo = FALSE}

comparisonsAir <- loggers |> filter(Recording == "Air") |> distinct(River, SFA)
comparisonsWater <- loggers |> filter(Recording == "Water" | Recording == "Level") |> distinct(River, SFA) |> filter(River %in% comparisonsAir$River)

watercheck <- loggers |> 
  filter(River %in% comparisonsWater$River)


############################################

RiverList1 <- unique(watercheck$River[watercheck$Recording == "Water"])
df1 <- data.frame()
for (i in 1:length(RiverList1)) {
  
  data <- watercheck |> 
  filter(River == RiverList1[i])

SNWater <- unique(data$Serial[data$Recording == "Water"])
SNAir <- unique(data$Serial[data$Recording == "Air"])


  for (i in 1:length(SNWater)) {
     # 
     # data1 <- data |> 
     #   filter(Serial == SNWater[i] | Serial == SNAir) |> 
     #   dplyr::select(River, Serial, Date.Time, Temp.C, Recording) |> 
     #   spread(Recording, Temp.C) |> 
     #   group_by(date(Date.Time)) |> 
     #   mutate(maxAir = max(Air)) |> 
     #   mutate(maxWater = max(Water)) |> 
     #   mutate(check = maxWater - maxAir) |> 
     #   mutate(keep = 1,
     #          keep = replace(keep, check > -1, 0)) |> 
     #   ungroup() |> 
       # dplyr::select(River, Serial, Date.Time, Water, Air, keep) |>
       # gather(key = "Recording", value = "Temp.C", c(Water, Air)) |>
       # filter(Recording != "Air") |>
       # filter(!is.na(Temp.C))


     data1 <- data |>
       filter(Serial == SNWater[i] | Serial == SNAir) |>
       mutate(Date = date(Date.Time)) |> 
       filter(!is.na(Temp.C)) |> 
       # mutate(ID = paste(Recording, Serial, sep = "_")) |> 
       dplyr::select(River, Date.Time, Date, Temp.C, Recording) |>
       spread(Recording, Temp.C) |>
       group_by(Date) |>
       mutate(maxAir = max(Air)) |>
       mutate(maxWater = max(Water)) |>
       mutate(check = maxWater - maxAir) |>
       mutate(keep = 1,
              keep = replace(keep, check > -1, 0)) |>
       ungroup() |> 
       dplyr::select(River, Date.Time, Water, Air, keep) |>
       gather(key = "Recording", value = "Temp.C", c(Water, Air)) |>
       mutate(Serial = NA,
              Serial = replace(Serial, Recording == "Water", SNWater[i]),
              Serial = replace(Serial, Recording == "Air", SNAir))

df1 <- rbind(df1, data1)
}   
  
}

RiverList2 <- unique(watercheck$River[watercheck$Recording == "Level"])
df2 <- data.frame()
for (i in 1:length(RiverList2)) {
  
  data <- watercheck |> 
  filter(River == RiverList2[i])

SNWater <- unique(data$Serial[data$Recording == "Level"])
SNAir <- unique(data$Serial[data$Recording == "Air"])


  for (i in 1:length(SNWater)) {
  
     # data2 <- data |>
     #   filter(Recording != "Water") |>
     #   dplyr::select(River, Serial, Date.Time, Temp.C, Recording) |>
     #   spread(Recording, Temp.C) |>
     #   group_by(date(Date.Time)) |>
     #   mutate(maxAir = max(Air)) |>
     #   mutate(maxWater = max(Level)) |>
     #   mutate(check = maxWater - maxAir) |>
     #   mutate(keep = 1,
     #          keep = replace(keep, check > -1, 0)) |>
     #   ungroup() |>
     #   dplyr::select(River, Serial, Date.Time, Level, Air, keep) |>
     #   gather(key = "Recording", value = "Temp.C", c(Level, Air)) |> 
     #   filter(Recording != "Air") |> 
     #   filter(!is.na(Temp.C))
     
      data2 <- data |>
       filter(Serial == SNWater[i] | Serial == SNAir) |>
       mutate(Date = date(Date.Time)) |> 
       filter(!is.na(Temp.C)) |> 
       # mutate(ID = paste(Recording, Serial, sep = "_")) |> 
       dplyr::select(River, Date.Time, Date, Temp.C, Recording) |>
       spread(Recording, Temp.C) |>
       group_by(Date) |>
       mutate(maxAir = max(Air)) |>
       mutate(maxWater = max(Level)) |>
       mutate(check = maxWater - maxAir) |>
       mutate(keep = 1,
              keep = replace(keep, check > -1, 0)) |>
       ungroup() |> 
       dplyr::select(River, Date.Time, Level, Air, keep) |>
       gather(key = "Recording", value = "Temp.C", c(Level, Air)) |>
       mutate(Serial = NA,
              Serial = replace(Serial, Recording == "Level", SNWater[i]),
              Serial = replace(Serial, Recording == "Air", SNAir))
     
df2 <- rbind(df2, data2)
}   
  
}

full <- bind_rows(df1, df2) |> 
  # filter(keep == 1) |>
  distinct() |> 
  filter(Recording != "Air") |> 
  filter(!is.na(Temp.C))

# check that all values from water temperature readings were retained
watercheck |> filter(Recording != "Air") |> filter(!is.na(Temp.C)) |> dim()

cleaned <- watercheck |> left_join(full) |> 
  mutate(keep = replace(keep, Recording == "Air", 1)) |> 
  filter(keep == 1)

ggplot() +
  geom_line(data = watercheck |> filter(Recording == "Air"), 
            aes(x = Date.Time, y = Temp.C),
            colour = 'red') +
  geom_line(data = watercheck |> filter(Recording == "Water"),
            aes(x = Date.Time, y = Temp.C),
            colour = 'blue') +
  facet_wrap(~River)

ggplot() +
  geom_line(data = cleaned |> filter(Recording == "Air"), 
            aes(x = Date.Time, y = Temp.C),
            colour = 'red') +
  geom_line(data = cleaned |> filter(Recording == "Water"),
            aes(x = Date.Time, y = Temp.C),
            colour = 'blue') +
  facet_wrap(~River)


```
### Need to determine the range between max air and max water when IN WATER
Its a rough estimate for now. need more modelling to better determine in and out of water (definitely related to oscillation)

# Next step is to incorporate level logger data

## still need river numbers